Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-07-08 supplementary.tex
modified fig s6 size
Fixed typo in legend of Fig S2

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_Hemato_Supp.png}
\caption[]{Analysis of hematopoietic differentiation. (A) Low dimensional embedding of single cells coloured by original cell type and pseudotime. (B) Cells are coloured according to the nSBM grouping at level 3 of the hierarchy, next to a radial tree representation of the same model.}\label{Figure_Hemato_Supp}
\end{figure}
\clearpage

@@

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=1\textheight]{FigureOptimalLevel.png}
\caption[]{Choice of the optimal hierarchy level. Datasets analysed for choice of the most relevant hierarchy level are represented here, from top to bottom in the same order as in Table \ref{table_optimal}. For each dataset we report the UMAP embedding coloured by the annotation given in the corresponding manuscript, the profile of modularity $Q$ at different level of the hierarchy and the UMAP embeddings coloured by the level according to $i^k$ or $i^Q$. The dashed line in modularity plots represents the modularity calculated using the annotation from the corresponding manuscripts.}\label{FigureOptimalLevel}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_Hemato_Supp.png}
\caption[]{Analysis of hematopoietic differentiation. (A) Low dimensional embedding of single cells coloured by original cell type and pseudotime. (B) Cells are coloured according to the nSBM grouping at level 1 of the hierarchy, next to a radial tree representation of the same model.}\label{Figure_Hemato_Supp}
\end{figure}
\clearpage

@@

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.9\textheight]{FigureOptimalLevel.png}
\caption[]{Choice of the optimal hierarchy level. Datasets analysed for choice of the most relevant hierarchy level are represented here, from top to bottom in the same order as in Table \ref{table_optimal}. For each dataset we report the UMAP embedding coloured by the annotation given in the corresponding manuscript, the profile of modularity $Q$ at different level of the hierarchy and the UMAP embeddings coloured by the level according to $i^k$ or $i^Q$. The dashed line in modularity plots represents the modularity calculated using the annotation from the corresponding manuscripts.}\label{FigureOptimalLevel}
\end{figure}
